---
title: "14_Checking and Merging"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
  code_folding: hide

---
Started January 12, 2021. 


`write_preg_dnam14.csv` from 11_Full_Sample_Size. 

It consists of the 
 * women who we have DNAm for in 2005
 * who also had pregnancies in the NSF study (nsfnumb>0)
 * and uses their maxnsfnumb (highest birth in the NSF study)

Note that I use `2017-12-01 file for Calen.dta` which is from Dan Eisenberg, from the original CoR paper (in projects, eAge, ...)  
This has the SES3 variable and the urbanicity variable (and genetic PCs) used in the original paper. 


```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(haven)
library(sjlabelled)
```


```{r}

# all_DBS_shipping_info <- read_csv("Output/Data/all_DBS_shipping_info.csv")
```
No point in having this I doubt. The DBS shipping info was incomplete and only so helpful and not necessarily related to the final pull. 


# Load Data
```{r}
Cebu_sample_reflist_for_Koborlab_update_08_2020 <- read_csv(here::here("Output/Data/Cebu_sample_reflist_for_Koborlab_update_08_2020.csv"),
col_types = cols(uncchdid = col_character()))

Cebu_sample_reflist_for_Koborlab_update_08_2020 <-Cebu_sample_reflist_for_Koborlab_update_08_2020 %>% 
  mutate(date = as_date(mdy(date))) %>% 
  mutate(Sample_Group = if_else(sample_type == "pregnancy", 
                               paste(uncchdid, "p", sep = "_"), 
                               paste(uncchdid, "b", sep = "_")))

```


# Pull Phenotype Data of interest
```{r}
preg_dnam14 <- read_csv(here::here("Output", "Data", "write_preg_dnam14.csv"), col_types = cols(uncchdid = col_character())) 

preg_dnam14
```

# Merge with other phenotypic data
urbanicity, SES score at pregnancy (), BMI? Smoking?
```{r}
assessdiet_20141016 <- read_dta(here::here("Data/2009_2014/Pregnancy/corrected Stata files/assessdiet_20141016.dta"))

```

Add anthropometrics
```{r}
assessdiet_20141016 <-assessdiet_20141016 %>%   
  na_if(., -9) %>%
#  mutate(whr = waist / hip) %>%   
  mutate(weight_nsf = rowMeans(select(., starts_with("weight")), na.rm = TRUE)) %>%  #
  mutate(armcircm_nsf = rowMeans(select(., starts_with("armcirc")), na.rm = TRUE)) %>%  #
  mutate(tricep_mean_nsf = rowMeans(select(., starts_with("tricep")), na.rm = TRUE)) %>%  # mean of 3 measurements in mm
  mutate(subscap_mean_nsf = rowMeans(select(., starts_with("subscap")), na.rm = TRUE)) %>%  # mean of 3 measurements in mm
  mutate(supra_mean_nsf = rowMeans(select(., starts_with("suprail")), na.rm = TRUE)) %>%  # mean of 3 measurements in mm
  mutate(arm_musc_circ_nsf = armcircm_nsf*10 - (tricep_mean_nsf * 3.14)) %>% # Upper arm muscle circ. (S) in mm: S = c - ( T * 3.14) 
  mutate(arm_musc_area_nsf = arm_musc_circ_nsf^2 / 12.56) %>% # Upper arm muscle area (M) in mm² : M = S² / 12.56
#  mutate(bmi = weight/(height/100)^2) %>% 
  mutate(skinfold_sum_nsf = subscap_mean_nsf + supra_mean_nsf + tricep_mean_nsf)
```

Make dates and select
```{r}
assessdiet_20141016$date_preg_anthro <-ymd(with(assessdiet_20141016, paste(as_numeric(yearmeas), as_numeric(monthmeas), as_numeric(daymeas), sep = "/")))

assessdiet_20141016_sub <-assessdiet_20141016 %>%
  mutate(uncchdid = as_character(uncchdid)) %>% 
  select(uncchdid, nsfnumb, date_preg_anthro, basebrgy:basewman,  weight_nsf, armcircm_nsf, subscap_mean_nsf, supra_mean_nsf, tricep_mean_nsf, arm_musc_area_nsf, skinfold_sum_nsf, hemoglob, diabetes)

```

## Add height for BMI
I could not find any height info for 2009, so I use 2005
```{r}
anthro05 <-read_dta(here::here("Data/2005/zip_child_2005/anthdiet.DTA")) %>% 
  as_character(uncchdid) %>% 
  rename_all(tolower) %>% 
  select(uncchdid, height)

assessdiet_20141016_sub <-left_join(assessdiet_20141016_sub, anthro05, by = "uncchdid") %>% 
 mutate(bmi = weight_nsf/(height/100)^2)
```

## Add smoking
```{r}
smoke <-read_dta(here::here("Data/2009_2014/Pregnancy/corrected Stata files/morhealt_20141016.dta"), col_select = c(uncchdid, smoke)) %>% 
  mutate(uncchdid = as_character(uncchdid))

# Remove the duplicates (not sure why there are numerous answers for 'smoke', but I will keep the one that is smoke yes)
smoke <-smoke %>% 
  group_by(uncchdid) %>%
  top_n(1, smoke) %>%
  distinct(uncchdid, smoke) %>% 
  arrange(uncchdid)


assessdiet_20141016_sub <-left_join(assessdiet_20141016_sub, smoke, by = "uncchdid")
```

## Get urbanicity and SES from 2005
I don't have urbanicity or an SES variable for 2009-2014, but I suspect that using 2005 is good enough. 

```{r}
dan.new <- read_dta(here::here("Data/Other/2017-12-01 file for Calen.dta"), col_select = c("uncchdid", "numbpreg", "icpc1", "icpc2", "icpc3", "icpc4", "icpc5", "icpc6", "icpc7", "icpc8", "icpc9", "icpc10", "SES3", "urbanicity")) %>% 
  mutate(uncchdid = as_character(uncchdid))
names(dan.new)

assessdiet_20141016_sub <-left_join(assessdiet_20141016_sub, dan.new, by = "uncchdid")

```

Remove duplicates
```{r}
assessdiet_20141016_sub <-assessdiet_20141016_sub %>% 
  distinct()
```



Pull only the pregnancies I need (nsfnumb)
```{r}
preg_all_57914_long <-read_csv(here::here("Output/Data", "preg_all_57914_long.csv"), 
                               col_types = cols(uncchdid = col_character())) %>%
  rename(pregord_presnf = pregord, 
         max_preg_ord_prensf = max.preg.ord, 
         pregord_all = new.preg, 
         max_preg_all = max.all.preg) %>% 
  select(-c(dayblood:yearblood)) 

# Oops, parsing issue. Someone didn't put 01, but "January".
preg_all_57914_long[1206, "monthdie"] <-1
```

```{r}
long_w_na <-preg_all_57914_long %>% 
  filter(is.na(yearprg) & nsf == "nsf")

long_w_na_uncchdid <-long_w_na %>% pull(uncchdid)
```

```{r}
preg_dnam14 %>% 
  filter(uncchdid %in% c(long_w_na_uncchdid))

```
Nobody who is missing data for NSF pregnancy is in the preg_dnam14 data. 
```{r}
Cebu_sample_reflist_for_Koborlab_update_08_2020 %>% 
  filter(sample_type == "pregnancy") %>% 
  nrow()
# 334

preg_dnam14 %>% 
  filter(!uncchdid %in% c(long_w_na_uncchdid)) %>% 
  nrow()
# 340

preg_all_57914_long %>% 
  nrow()
# 1271
```


```{r}
intersect(names(Cebu_sample_reflist_for_Koborlab_update_08_2020), names(preg_dnam14))
# uncchdid
intersect(names(Cebu_sample_reflist_for_Koborlab_update_08_2020), names(preg_all_57914_long))
# uncchdid

intersect(names(preg_dnam14), names(preg_all_57914_long))


inter_sample_preg <-left_join(Cebu_sample_reflist_for_Koborlab_update_08_2020, 
          preg_dnam14, by = "uncchdid")


full_nsf_data <-right_join(preg_all_57914_long, 
                          inter_sample_preg, 
                          by = c("uncchdid", "nsfnumb", "iccuncid"))


```

Find TWINS and remove them (2 sets, 1 woman has both birth and pregnancy, so total 3 extra)
```{r}
full_nsf_data %>% 
  filter(Sample_Group %in% c("20665_b", "20665_p", "23267_p")) %>% 
  select(outcome)

full_nsf_data <-full_nsf_data %>% 
  distinct(Sample_Group, .keep_all = TRUE)

full_nsf_data %>% 
  filter(uncchdid == "23157") %>% glimpse()


```

Add birthdays for age at sample calculation
```{r}
merged_bday <-read_csv(here::here("Data/Other/merged_bday.csv"))

full_nsf_data <-left_join(full_nsf_data, 
          merged_bday %>%
            as_character(uncchdid) %>% 
            select(uncchdid, bday), by = "uncchdid") 


full_nsf_data <-full_nsf_data %>% 
  mutate(age_nsf_sample = lubridate::time_length(date - bday, unit = "years"))
           

full_nsf_data <-full_nsf_data %>% 
  distinct(Sample_Group, .keep_all = TRUE) 
```



```{r}
covariate_merge <-intersect(names(full_nsf_data), names(assessdiet_20141016_sub))

full_nsf_w_covariates <-left_join(full_nsf_data, assessdiet_20141016_sub, by = c(covariate_merge)) %>% 
  select(-ends_with(".y"))

write_csv(full_nsf_w_covariates, here::here("Output", "Data", "full_nsf_w_covariates.csv"))


```










