---
title: "EDA_Phenotypic_Preliminary"
author: "Raviraj Rege"
date: "7/21/2021"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
#Loading packages
library(tidyverse)
library(janitor)
library(skimr)
library(corrplot)
library(RColorBrewer)
library(haven)
here::here()
#Reading and Updating data
raw_pheno <- read_csv(file = here::here("Data/Phenotypic_Data/full_nsf_w_covariates.csv")) %>%
  clean_names()
curr_preg <- read_dta(file = here::here("Data/Phenotypic_Data/final NSF IC Female Pregnancy Tracking files/Pregnancy files/corrected Stata files/currpreg20141016.dta")) %>%
  clean_names %>%
  select(uncchdid, lmpdate)
```

## Combining in Raw Data for Usable Data

```{r}
usable_pheno <- raw_pheno %>%
  select(uncchdid, monthprg, dayprg, yearprg, sample_group, sample_type, iccsex, date_prg_term, hour, minute, am_pm, sourcewt, date_icc_meas, icc_weight_birth, icc_length_home, icc_weight_home, icc_armcircm_home, icc_tricep_mean_home, icc_bicep_mean_home, icc_subscap_mean_home, icc_supra_mean_home, icc_calf_mean_home, icc_thigh_mean_home, icc_headcirc_mean_home, icc_abdom_mean_home) %>%
  filter(sample_type == "pregnancy") %>%
  mutate(icc_total_skin_mean_home = icc_tricep_mean_home + icc_bicep_mean_home + icc_subscap_mean_home + icc_supra_mean_home + icc_calf_mean_home + icc_thigh_mean_home) %>%
  full_join(curr_preg, key = uncchdid) %>%
  mutate(gestational_age = date_prg_term - lmpdate, measurement_age = date_icc_meas - date_prg_term)
```

## Summary Statistics Overview

```{r}
skimr::skim(usable_pheno)
```

## Distribution of Birth Weight

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = icc_weight_birth)) +
  geom_histogram()
```

## Distribution of Length Measured at Home

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = icc_length_home)) +
  geom_histogram()
```

## Distribution of Weight Measured at Home

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = icc_weight_home)) +
  geom_histogram()
```

## Distribution of Arm Circumference Measured at Home

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = icc_armcircm_home)) +
  geom_histogram()
```

## Distribution of Total Skin Fold Thickness Measured at Home

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = icc_total_skin_mean_home)) +
  geom_histogram()
```

## Distribution of Head Circumference Measured at Home

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = icc_headcirc_mean_home)) +
  geom_histogram()
```

## Distribution of Abdominal Circumference Measured at Home

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = icc_abdom_mean_home)) +
  geom_histogram()
```

## Distribution of Gestational Age at Birth (Date of End of Pregnancy - Date of Last Menstrual Period)

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = gestational_age)) +
  geom_histogram()
```

## Distribution of Age at Measurement at Home (Date of Measurement - Date of End of Pregnancy)

```{r}
usable_pheno %>%
  ggplot(mapping = aes(x = measurement_age)) +
  geom_histogram()
```

## Correlation Plot between various Phenotypic Variables

```{r}
usable_pheno2 <- usable_pheno %>% select(icc_weight_birth, icc_length_home, icc_weight_home, icc_armcircm_home, icc_headcirc_mean_home, icc_abdom_mean_home, icc_total_skin_mean_home)
M <- cor(usable_pheno2, use = "complete.obs")
corrplot(M, type="upper", order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))
```

