---
title: "Seconday Analysis"
author: "Raviraj Rege"
date: "9/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r echo=TRUE}
# Loading packages
library(tidyverse)
library(lubridate)
library(janitor)
library(skimr)
library(corrplot)
library(haven)
library(ggpubr)
library(sjlabelled)
library(sjPlot)

# Create new dataset
combined_data <- read_csv(here::here("Data/combined_final_data.csv"))
```

# Initial Set of Model Analyses

No Pre-BMI adjustments, IEAA
```{r, eval = FALSE}
## No Pre-BMI adjustments, IEAA
ieaa_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ ieaa_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

ieaa_pregresid_no_bmi_icc_length_home <- update(ieaa_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

ieaa_pregresid_no_bmi_icc_armcircm_home <- update(ieaa_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

ieaa_pregresid_no_bmi_icc_abdom_mean_home <- update(ieaa_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

ieaa_pregresid_no_bmi_icc_headcirc_mean_home <- update(ieaa_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

ieaa_pregresid_no_bmi_icc_total_skin_mean_home <- update(ieaa_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(ieaa_pregresid_no_bmi_icc_weight_home, ieaa_pregresid_no_bmi_icc_length_home, ieaa_pregresid_no_bmi_icc_armcircm_home, ieaa_pregresid_no_bmi_icc_abdom_mean_home, ieaa_pregresid_no_bmi_icc_headcirc_mean_home, ieaa_pregresid_no_bmi_icc_total_skin_mean_home)
```

<br><br>

## No Pre-BMI adjustments, EEAA
```{r, eval = FALSE}
## No Pre-BMI adjustments, EEAA
eeaa_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ eeaa_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

eeaa_pregresid_no_bmi_icc_length_home <- update(eeaa_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

eeaa_pregresid_no_bmi_icc_armcircm_home <- update(eeaa_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

eeaa_pregresid_no_bmi_icc_abdom_mean_home <- update(eeaa_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

eeaa_pregresid_no_bmi_icc_headcirc_mean_home <- update(eeaa_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

eeaa_pregresid_no_bmi_icc_total_skin_mean_home <- update(eeaa_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(eeaa_pregresid_no_bmi_icc_weight_home, eeaa_pregresid_no_bmi_icc_length_home, eeaa_pregresid_no_bmi_icc_armcircm_home, eeaa_pregresid_no_bmi_icc_abdom_mean_home, eeaa_pregresid_no_bmi_icc_headcirc_mean_home, eeaa_pregresid_no_bmi_icc_total_skin_mean_home)
```

<br><br>

 No Pre-BMI adjustments, pheno_pregresidage
```{r, eval = FALSE}
## No Pre-BMI adjustments, pheno_pregresidage
age_accel_pheno_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ age_accel_pheno_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

age_accel_pheno_pregresid_no_bmi_icc_length_home <- update(age_accel_pheno_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

age_accel_pheno_pregresid_no_bmi_icc_armcircm_home <- update(age_accel_pheno_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

age_accel_pheno_pregresid_no_bmi_icc_abdom_mean_home <- update(age_accel_pheno_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

age_accel_pheno_pregresid_no_bmi_icc_headcirc_mean_home <- update(age_accel_pheno_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

age_accel_pheno_pregresid_no_bmi_icc_total_skin_mean_home <- update(age_accel_pheno_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(age_accel_pheno_pregresid_no_bmi_icc_weight_home, age_accel_pheno_pregresid_no_bmi_icc_length_home, age_accel_pheno_pregresid_no_bmi_icc_armcircm_home, age_accel_pheno_pregresid_no_bmi_icc_abdom_mean_home, age_accel_pheno_pregresid_no_bmi_icc_headcirc_mean_home, age_accel_pheno_pregresid_no_bmi_icc_total_skin_mean_home)
```

<br><br>

 No Pre-BMI adjustments, Grimage
```{r, eval = FALSE}
## No Pre-BMI adjustments, grimage
age_accel_grim_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ age_accel_grim_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

age_accel_grim_pregresid_no_bmi_icc_length_home <- update(age_accel_grim_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

age_accel_grim_pregresid_no_bmi_icc_armcircm_home <- update(age_accel_grim_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

age_accel_grim_pregresid_no_bmi_icc_abdom_mean_home <- update(age_accel_grim_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

age_accel_grim_pregresid_no_bmi_icc_headcirc_mean_home <- update(age_accel_grim_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

age_accel_grim_pregresid_no_bmi_icc_total_skin_mean_home <- update(age_accel_grim_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(age_accel_grim_pregresid_no_bmi_icc_weight_home, age_accel_grim_pregresid_no_bmi_icc_length_home, age_accel_grim_pregresid_no_bmi_icc_armcircm_home, age_accel_grim_pregresid_no_bmi_icc_abdom_mean_home, age_accel_grim_pregresid_no_bmi_icc_headcirc_mean_home, age_accel_grim_pregresid_no_bmi_icc_total_skin_mean_home)
```

<br><br>

## Pre-BMI adjustments, IEAA
```{r}
## Pre-BMI adjustments, IEAA
ieaa_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ ieaa_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

ieaa_pregresid_bmi_icc_length_home <- update(ieaa_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

ieaa_pregresid_bmi_icc_armcircm_home <- update(ieaa_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

ieaa_pregresid_bmi_icc_abdom_mean_home <- update(ieaa_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

ieaa_pregresid_bmi_icc_headcirc_mean_home <- update(ieaa_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

ieaa_pregresid_bmi_icc_total_skin_mean_home <- update(ieaa_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(ieaa_pregresid_bmi_icc_weight_home, ieaa_pregresid_bmi_icc_length_home, ieaa_pregresid_bmi_icc_armcircm_home, ieaa_pregresid_bmi_icc_abdom_mean_home, ieaa_pregresid_bmi_icc_headcirc_mean_home, ieaa_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S3_IEAA_other.doc"))
```

<br><br>

## Pre-BMI adjustments, eeaa_id
```{r}
## Pre-BMI adjustments, EEAA
eeaa_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ eeaa_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

eeaa_pregresid_bmi_icc_length_home <- update(eeaa_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

eeaa_pregresid_bmi_icc_armcircm_home <- update(eeaa_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

eeaa_pregresid_bmi_icc_abdom_mean_home <- update(eeaa_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

eeaa_pregresid_bmi_icc_headcirc_mean_home <- update(eeaa_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

eeaa_pregresid_bmi_icc_total_skin_mean_home <- update(eeaa_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(eeaa_pregresid_bmi_icc_weight_home, eeaa_pregresid_bmi_icc_length_home, eeaa_pregresid_bmi_icc_armcircm_home, eeaa_pregresid_bmi_icc_abdom_mean_home, eeaa_pregresid_bmi_icc_headcirc_mean_home, eeaa_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S4_EEAA_other.doc"))
```

<br><br>

## Pre-BMI adjustments, phenoage
```{r}
## Pre-BMI adjustments, phenoage
age_accel_pheno_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ age_accel_pheno_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

age_accel_pheno_pregresid_bmi_icc_length_home <- update(age_accel_pheno_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

age_accel_pheno_pregresid_bmi_icc_armcircm_home <- update(age_accel_pheno_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

age_accel_pheno_pregresid_bmi_icc_abdom_mean_home <- update(age_accel_pheno_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

age_accel_pheno_pregresid_bmi_icc_headcirc_mean_home <- update(age_accel_pheno_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

age_accel_pheno_pregresid_bmi_icc_total_skin_mean_home <- update(age_accel_pheno_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(age_accel_pheno_pregresid_bmi_icc_weight_home, age_accel_pheno_pregresid_bmi_icc_length_home, age_accel_pheno_pregresid_bmi_icc_armcircm_home, age_accel_pheno_pregresid_bmi_icc_abdom_mean_home, age_accel_pheno_pregresid_bmi_icc_headcirc_mean_home, age_accel_pheno_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S5_pheno_other.doc"))
```

<br><br>

## Pre-BMI adjustments, grimage
```{r}
## Pre-BMI adjustments, grimage
age_accel_grim_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ age_accel_grim_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

age_accel_grim_pregresid_bmi_icc_length_home <- update(age_accel_grim_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

age_accel_grim_pregresid_bmi_icc_armcircm_home <- update(age_accel_grim_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

age_accel_grim_pregresid_bmi_icc_abdom_mean_home <- update(age_accel_grim_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

age_accel_grim_pregresid_bmi_icc_headcirc_mean_home <- update(age_accel_grim_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

age_accel_grim_pregresid_bmi_icc_total_skin_mean_home <- update(age_accel_grim_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(age_accel_grim_pregresid_bmi_icc_weight_home, age_accel_grim_pregresid_bmi_icc_length_home, age_accel_grim_pregresid_bmi_icc_armcircm_home, age_accel_grim_pregresid_bmi_icc_abdom_mean_home, age_accel_grim_pregresid_bmi_icc_headcirc_mean_home, age_accel_grim_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S6_grim_other.doc"))

```

**Overall conclusion: GrimAge looks the best, now going to try to dissect each of the individual "clocks" that make up GrimAge.**

# Secondary Set of Model Analyses (Focused on Components of GrimAge)

No Pre-BMI adjustments, dn_am_adm_adj_age
```{r, eval = FALSE}
## No Pre-BMI adjustments, dn_am_adm_adj_age
dn_am_adm_adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_adm_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_adm_adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_adm_adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_adm_adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_adm_adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_adm_adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_adm_adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_adm_adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_adm_adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_adm_adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_adm_adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_adm_adj_age_pregresid_no_bmi_icc_weight_home, dn_am_adm_adj_age_pregresid_no_bmi_icc_length_home, dn_am_adm_adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_adm_adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_adm_adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_adm_adj_age_pregresid_no_bmi_icc_total_skin_mean_home)
```

<br><br>

## Pre-BMI adjustments, dn_am_adm_adj_age

<br>

```{r}
## Pre-BMI adjustments, dn_am_adm_adj_age
dn_am_adm_adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_adm_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_adm_adj_age_pregresid_bmi_icc_length_home <- update(dn_am_adm_adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_adm_adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_adm_adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_adm_adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_adm_adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_adm_adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_adm_adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_adm_adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_adm_adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_adm_adj_age_pregresid_bmi_icc_weight_home, dn_am_adm_adj_age_pregresid_bmi_icc_length_home, dn_am_adm_adj_age_pregresid_bmi_icc_armcircm_home, dn_am_adm_adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_adm_adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_adm_adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S7_adm_other.doc"))
```

<br><br>

 No Pre-BMI adjustments, dn_am_b2m_adj_age
<br>

```{r, eval = FALSE}
## No Pre-BMI adjustments, dn_am_b2m_adj_age
dn_am_b2m_adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_b2m_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_b2m_adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_b2m_adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_b2m_adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_b2m_adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_b2m_adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_b2m_adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_b2m_adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_b2m_adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_b2m_adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_b2m_adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_b2m_adj_age_pregresid_no_bmi_icc_weight_home, dn_am_b2m_adj_age_pregresid_no_bmi_icc_length_home, dn_am_b2m_adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_b2m_adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_b2m_adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_b2m_adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```

<br><br>

## Pre-BMI adjustments, dn_am_b2m_adj_age
<br>

```{r} 
## Pre-BMI adjustments, dn_am_b2m_adj_age
dn_am_b2m_adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_b2m_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_b2m_adj_age_pregresid_bmi_icc_length_home <- update(dn_am_b2m_adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_b2m_adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_b2m_adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_b2m_adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_b2m_adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_b2m_adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_b2m_adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_b2m_adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_b2m_adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_b2m_adj_age_pregresid_bmi_icc_weight_home, dn_am_b2m_adj_age_pregresid_bmi_icc_length_home, dn_am_b2m_adj_age_pregresid_bmi_icc_armcircm_home, dn_am_b2m_adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_b2m_adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_b2m_adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S8_b2m_other.doc"))

```   

<br><br>

 No Pre-BMI adjustments, dn_am_cystatin_c_adj_age
<br>

```{r, eval = FALSE} 
## No Pre-BMI adjustments, dn_am_cystatin_c_adj_age
dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_cystatin_c_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_weight_home, dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_length_home, dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_cystatin_c_adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```

<br><br>

## Pre-BMI adjustments, dn_am_cystatin_c_adj_age
<br>

```{r} 
## Pre-BMI adjustments, dn_am_cystatin_c_adj_age
dn_am_cystatin_c_adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_cystatin_c_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_cystatin_c_adj_age_pregresid_bmi_icc_length_home <- update(dn_am_cystatin_c_adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_cystatin_c_adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_cystatin_c_adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_cystatin_c_adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_cystatin_c_adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_cystatin_c_adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_cystatin_c_adj_age_pregresid_bmi_icc_weight_home, dn_am_cystatin_c_adj_age_pregresid_bmi_icc_length_home, dn_am_cystatin_c_adj_age_pregresid_bmi_icc_armcircm_home, dn_am_cystatin_c_adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_cystatin_c_adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_cystatin_c_adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S9_cystatin_other.doc"))

```

<br><br>

 No Pre-BMI adjustments, dn_am_gdf15adj_age_pregresid
<br>

```{r, eval = FALSE} 
## No Pre-BMI adjustments, dn_am_gdf15adj_age
dn_am_gdf15adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_gdf15adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_gdf15adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_gdf15adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_gdf15adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_gdf15adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_gdf15adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_gdf15adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_gdf15adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_gdf15adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_gdf15adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_gdf15adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_gdf15adj_age_pregresid_no_bmi_icc_weight_home, dn_am_gdf15adj_age_pregresid_no_bmi_icc_length_home, dn_am_gdf15adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_gdf15adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_gdf15adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_gdf15adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```  

<br><br>

## Pre-BMI adjustments, dn_am_gdf15adj_age
<br>

```{r} 
## Pre-BMI adjustments, dn_am_gdf15adj_age
dn_am_gdf15adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_gdf15adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_gdf15adj_age_pregresid_bmi_icc_length_home <- update(dn_am_gdf15adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_gdf15adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_gdf15adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_gdf15adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_gdf15adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_gdf15adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_gdf15adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_gdf15adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_gdf15adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_gdf15adj_age_pregresid_bmi_icc_weight_home, dn_am_gdf15adj_age_pregresid_bmi_icc_length_home, dn_am_gdf15adj_age_pregresid_bmi_icc_armcircm_home, dn_am_gdf15adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_gdf15adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_gdf15adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S10_gdf15_other.doc"))

```   

<br><br>

No Pre-BMI adjustments, dn_am_leptin_adj_age_pregresid
<br>

```{r, eval = FALSE} 
## No Pre-BMI adjustments, dn_am_leptin_adj_age
dn_am_leptin_adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_leptin_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_leptin_adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_leptin_adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_leptin_adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_leptin_adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_leptin_adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_leptin_adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_leptin_adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_leptin_adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_leptin_adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_leptin_adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_leptin_adj_age_pregresid_no_bmi_icc_weight_home, dn_am_leptin_adj_age_pregresid_no_bmi_icc_length_home, dn_am_leptin_adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_leptin_adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_leptin_adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_leptin_adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```   

<br><br>

## Pre-BMI adjustments, dn_am_leptin_adj_age
<br>

```{r} 
## Pre-BMI adjustments, dn_am_leptin_adj_age
dn_am_leptin_adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_leptin_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_leptin_adj_age_pregresid_bmi_icc_length_home <- update(dn_am_leptin_adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_leptin_adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_leptin_adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_leptin_adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_leptin_adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_leptin_adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_leptin_adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_leptin_adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_leptin_adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_leptin_adj_age_pregresid_bmi_icc_weight_home, dn_am_leptin_adj_age_pregresid_bmi_icc_length_home, dn_am_leptin_adj_age_pregresid_bmi_icc_armcircm_home, dn_am_leptin_adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_leptin_adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_leptin_adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S11_leptin_other.doc"))

```   

<br><br>

 No Pre-BMI adjustments, dn_am_packyrs_adj_age
<br>

```{r, eval = FALSE} 
## No Pre-BMI adjustments, dn_am_packyrs_adj_age
dn_am_packyrs_adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_packyrs_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_packyrs_adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_packyrs_adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_packyrs_adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_packyrs_adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_packyrs_adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_packyrs_adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_packyrs_adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_packyrs_adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_packyrs_adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_packyrs_adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_packyrs_adj_age_pregresid_no_bmi_icc_weight_home, dn_am_packyrs_adj_age_pregresid_no_bmi_icc_length_home, dn_am_packyrs_adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_packyrs_adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_packyrs_adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_packyrs_adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```   

<br><br>

## Pre-BMI adjustments, dn_am_packyrs_adj_age_pregresid
<br>

```{r} 
## Pre-BMI adjustments, dn_am_packyrs_adj_age
dn_am_packyrs_adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_packyrs_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_packyrs_adj_age_pregresid_bmi_icc_length_home <- update(dn_am_packyrs_adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_packyrs_adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_packyrs_adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_packyrs_adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_packyrs_adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_packyrs_adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_packyrs_adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_packyrs_adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_packyrs_adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_packyrs_adj_age_pregresid_bmi_icc_weight_home, dn_am_packyrs_adj_age_pregresid_bmi_icc_length_home, dn_am_packyrs_adj_age_pregresid_bmi_icc_armcircm_home, dn_am_packyrs_adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_packyrs_adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_packyrs_adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S12_packyears_other.doc"))

```   

<br><br>

No Pre-BMI adjustments, dn_am_pai1adj_age
<br>

```{r, eval = FALSE} 
## No Pre-BMI adjustments, dn_am_pai1adj_age
dn_am_pai1adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_pai1adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_pai1adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_pai1adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_pai1adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_pai1adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_pai1adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_pai1adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_pai1adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_pai1adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_pai1adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_pai1adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_pai1adj_age_pregresid_no_bmi_icc_weight_home, dn_am_pai1adj_age_pregresid_no_bmi_icc_length_home, dn_am_pai1adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_pai1adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_pai1adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_pai1adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```   

<br><br>

## Pre-BMI adjustments, dn_am_pai1adj_age
<br>

```{r} 
## Pre-BMI adjustments, dn_am_pai1adj_age
dn_am_pai1adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_pai1adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_pai1adj_age_pregresid_bmi_icc_length_home <- update(dn_am_pai1adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_pai1adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_pai1adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_pai1adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_pai1adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_pai1adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_pai1adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_pai1adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_pai1adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_pai1adj_age_pregresid_bmi_icc_weight_home, dn_am_pai1adj_age_pregresid_bmi_icc_length_home, dn_am_pai1adj_age_pregresid_bmi_icc_armcircm_home, dn_am_pai1adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_pai1adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_pai1adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S13_pai1_other.doc"))

```   

<br><br>

 No Pre-BMI adjustments, dn_am_timp1adj_age
<br>

```{r, eval = FALSE} 
## No Pre-BMI adjustments, dn_am_timp1adj_age
dn_am_timp1adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_timp1adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_timp1adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_timp1adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_timp1adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_timp1adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_timp1adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_timp1adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_timp1adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_timp1adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_timp1adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_timp1adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_timp1adj_age_pregresid_no_bmi_icc_weight_home, dn_am_timp1adj_age_pregresid_no_bmi_icc_length_home, dn_am_timp1adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_timp1adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_timp1adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_timp1adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```   

<br><br>

## Pre-BMI adjustments, dn_am_timp1adj_age
<br>

```{r} 
## Pre-BMI adjustments, dn_am_timp1adj_age
dn_am_timp1adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_timp1adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_timp1adj_age_pregresid_bmi_icc_length_home <- update(dn_am_timp1adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_timp1adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_timp1adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_timp1adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_timp1adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_timp1adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_timp1adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_timp1adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_timp1adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_timp1adj_age_pregresid_bmi_icc_weight_home, dn_am_timp1adj_age_pregresid_bmi_icc_length_home, dn_am_timp1adj_age_pregresid_bmi_icc_armcircm_home, dn_am_timp1adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_timp1adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_timp1adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S14_timp1_other.doc"))

```

<br><br>

 No Pre-BMI adjustments, dn_am_tl_adj_age
<br>

```{r, eval = FALSE} 
## No Pre-BMI adjustments, dn_am_tl_adj_age
dn_am_tl_adj_age_pregresid_no_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_tl_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1,data = combined_data)

dn_am_tl_adj_age_pregresid_no_bmi_icc_length_home <- update(dn_am_tl_adj_age_pregresid_no_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_tl_adj_age_pregresid_no_bmi_icc_armcircm_home <- update(dn_am_tl_adj_age_pregresid_no_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_tl_adj_age_pregresid_no_bmi_icc_abdom_mean_home <- update(dn_am_tl_adj_age_pregresid_no_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_tl_adj_age_pregresid_no_bmi_icc_headcirc_mean_home <- update(dn_am_tl_adj_age_pregresid_no_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_tl_adj_age_pregresid_no_bmi_icc_total_skin_mean_home <- update(dn_am_tl_adj_age_pregresid_no_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_tl_adj_age_pregresid_no_bmi_icc_weight_home, dn_am_tl_adj_age_pregresid_no_bmi_icc_length_home, dn_am_tl_adj_age_pregresid_no_bmi_icc_armcircm_home, dn_am_tl_adj_age_pregresid_no_bmi_icc_abdom_mean_home, dn_am_tl_adj_age_pregresid_no_bmi_icc_headcirc_mean_home, dn_am_tl_adj_age_pregresid_no_bmi_icc_total_skin_mean_home)

```   

<br><br>

## Pre-BMI adjustments, dn_am_tl_adj_age
<br>

```{r} 
## Pre-BMI adjustments, dn_am_tl_adj_age
dn_am_tl_adj_age_pregresid_bmi_icc_weight_home <- lm(icc_weight_home ~ dn_am_tl_adj_age_pregresid + gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

dn_am_tl_adj_age_pregresid_bmi_icc_length_home <- update(dn_am_tl_adj_age_pregresid_bmi_icc_weight_home, icc_length_home ~ .)

dn_am_tl_adj_age_pregresid_bmi_icc_armcircm_home <- update(dn_am_tl_adj_age_pregresid_bmi_icc_weight_home, icc_armcircm_home ~ .)

dn_am_tl_adj_age_pregresid_bmi_icc_abdom_mean_home <- update(dn_am_tl_adj_age_pregresid_bmi_icc_weight_home, icc_abdom_mean_home ~ .)

dn_am_tl_adj_age_pregresid_bmi_icc_headcirc_mean_home <- update(dn_am_tl_adj_age_pregresid_bmi_icc_weight_home, icc_headcirc_mean_home ~ .)

dn_am_tl_adj_age_pregresid_bmi_icc_total_skin_mean_home <- update(dn_am_tl_adj_age_pregresid_bmi_icc_weight_home, icc_total_skin_mean_home ~ .)

sjPlot::tab_model(dn_am_tl_adj_age_pregresid_bmi_icc_weight_home, dn_am_tl_adj_age_pregresid_bmi_icc_length_home, dn_am_tl_adj_age_pregresid_bmi_icc_armcircm_home, dn_am_tl_adj_age_pregresid_bmi_icc_abdom_mean_home, dn_am_tl_adj_age_pregresid_bmi_icc_headcirc_mean_home, dn_am_tl_adj_age_pregresid_bmi_icc_total_skin_mean_home,  show.est = FALSE, show.se = FALSE, show.stat = TRUE, show.std = TRUE, file = here::here("Output/Figures", "Table S15_tl_other.doc"))

```

# Figures

## Leptin and head circumference

### Get residuals
```{r}
# Get residuals
# 
length_basic <- lm(icc_length_home ~ gestage + measurement_age + iccsex + ses_pc1 + prebmiz,data = combined_data)

headcirc_basic <-update(length_basic, icc_headcirc_mean_home ~ . )

weight_basic <-update(length_basic, icc_weight_home ~ . )

length_resids <-broom::augment(length_basic)$.resid
headcirc_resids <-broom::augment(headcirc_basic)$.resid
weight_resids <-broom::augment(weight_basic)$.resid


```


### Make figures
```{r, fig.height = 8, fig.width = 9.5, eval = FALSE}
all_but_leptin_gest_age_no_meas <- lm(gestage ~ iccsex + ses_pc1 + prebmiz ,data = combined_data)

ga_resids <-broom::augment(all_but_leptin_gest_age_no_meas)$.resid



leptin_plot <-ggplot(data = combined_data, mapping = aes(x = dn_am_leptin_adj_age_pregresid, y = ga_resids)) +
  geom_point(color = 'firebrick', alpha = 0.7) +
  geom_smooth(method = "lm", color = "black") +
  labs(x = "DNAmLeptin EEA", y = "Postnatal Measured Weight (residuals)")+
  theme_pubr()+
  annotate("text", x = -2800, y = -50, label=expression(beta *  "= -0.15,  p-value = 0.009")); leptin_plot


adm_weight_plot <-ggplot(data = combined_data, mapping = aes(x = dn_am_adm_adj_age_pregresid, y = weight_resids)) +
  geom_point(color = 'steelblue', alpha = 0.7) +
  geom_smooth(method = "lm", color = "black") +
  labs(x = "DNAmADM EEA", y = "Postnatal Measured Weight (residuals)")+
  theme_pubr()+
  annotate("text", x = -28, y = -1.3, label=expression(beta *  "= 0.09,  p-value = 0.102")); adm_weight_plot

adm_length_plot <-ggplot(data = combined_data, mapping = aes(x = dn_am_adm_adj_age_pregresid, y = length_resids)) +
  geom_point(color = 'steelblue', alpha = 0.7) +
  geom_smooth(method = "lm", color = "black") +
  labs(x = "DNAmADM EEA", y = "Postnatal Length (residuals)")+
  theme_pubr()+
    annotate("text", x = -28, y = -10, label=expression(beta *  "= 0.14,  p-value = 0.013")); adm_length_plot


adm_headcirc_plot <-ggplot(data = combined_data, mapping = aes(x = dn_am_adm_adj_age_pregresid, y = headcirc_resids)) +
  geom_point(color = 'steelblue', alpha = 0.7) +
  geom_smooth(method = "lm", color = "black") +
  labs(x = "DNAmADM EEA", y = "Postnatal Head Circumference (residuals)")+
  theme_pubr()+
  annotate("text", x = -28, y = -4.5, label=expression(beta *  "= 0.09,  p-value = 0.086")); adm_headcirc_plot


ggarrange(leptin_plot, adm_length_plot, adm_headcirc_plot, adm_weight_plot,  
          labels = c("A", "B", "C", "D"), 
          ncol = 2, nrow = 2)


```

### Get Grim and TL residuals
```{r, fig.height = 5, fig.width = 13, eval = FALSE}
# Get residuals
length_resids <-broom::augment(length_basic)$.resid
headcirc_resids <-broom::augment(headcirc_basic)$.resid
TL_headcirc_plot <-broom::augment(headcirc_basic)$.resid

grim_length_plot <-ggplot(data = combined_data, mapping = aes(x = age_accel_grim_pregresid, y = length_resids)) +
  geom_point(color = 'purple', alpha = 0.7) +
  geom_smooth(method = "lm", color = "black") +
  labs(x = "DNAmGrim EEA", y = "Postnatal Length (residuals)")+
  theme_pubr()+
    annotate("text", x = -3.5, y = -10, label=expression(beta *  "= 0.14,  p-value = 0.013")); grim_length_plot


grim_headcirc_plot <-ggplot(data = combined_data, mapping = aes(x = age_accel_grim_pregresid, y = headcirc_resids)) +
  geom_point(color = 'purple', alpha = 0.7) +
  geom_smooth(method = "lm", color = "black") +
  labs(x = "DNAmGrim EEA", y = "Postnatal Head Circumference (residuals)")+
  theme_pubr()+
  annotate("text", x = -3.5, y = -4.5, label=expression(beta *  "= 0.09,  p-value = 0.086")); grim_headcirc_plot


TL_headcirc_plot <-ggplot(data = combined_data, mapping = aes(x = dn_am_tl_adj_age_pregresid, y = headcirc_resids)) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_smooth(method = "lm", color = "black") +
  labs(x = "DNAmTL EEA", y = "Postnatal Head Circumference (residuals)")+
  theme_pubr()+
  annotate("text", x = -0.125, y = -4.5, label=expression(beta *  "= 0.09,  p-value = 0.086")); TL_headcirc_plot

ggarrange(grim_length_plot, grim_headcirc_plot, TL_headcirc_plot,  
          labels = c("A", "B", "C"), 
          ncol = 3, nrow = 1)
```

